THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH III : MEASURING CHROMATICITY OF PROTOTYPE ELEMENT WITH REFLECTOMETRY.

### 2016-11-08 DishReflectometry/Paper1_v4.tex
Revised section 6.

    \title{THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY. } 
    %\maketitle

    \author{
    Nipanjana Patra\UCB\myemail,
    Aaron~R.~Parsons\UCB,
    David~R.~DeBoer\UCB,
    Nithyanandan Thyagarajan\ASU,
    Aaron  Ewall-Wice\altaffilmark{7},
    Gilbert Hsyu\UCB, 
    Tsz Kuk Leung\UCB,
    James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Anna Lebedeva\UCB, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
    }

@@

    \begin{abstract}
    Spectral structure from instrumental systematics is the current
    limiting factor for the experiments attempting to detect the redshifted 21~cm
    signal from the Epoch of Reionization (EoR). 
    Recent advances in the delay spectrum methodology for measuring the
    21~cm EoR power spectrum have brought new attention to the impact that
    an antenna's frequency performance has on the viability of
    making this challenging measurement.
    %Systematics are specific to
    %instruments and their direct measurement or estimation is not always
    %straightforward. 
    %The Hydrogen Epoch of Reionization Array (HERA) uses the delay
    %spectrum technique for estimating of 21~cm power spectrum. 
    In particular, it provides straightforward relationship
    between time-domain reflectrometry profiles that can be directly
    measured with a vector network analyzer (VNA) and the power spectrum modes accessible
    to a 21~cm EoR experiment.
    %In a unique way, the
    %delay spectrum technique directly translates to reflectometry in case of
    %measuring instrumental response and allows the direct measurement of systematic
    %effects in individual array element.  
    In this paper, we derive the explicit relationship between $S_{11}$ measurements
    made by a VNA and the extent of sidelobes of bright foregrounds in delay space.
    Using this formalism, we examine
    the spectral chromaticity of the prototype antenna elements that
    constitute Hydrogen Epoch of Reionization Array (HERA) 
    between 100 and 200~MHz.
    These reflectometry measurements exhibit spurious structure relative
    to electromagnetic simulations, but we find 
    that even without compensating for this structure, the antenna element
    will support measuring $k$ modes with line-of-sight components of
    $k_{\parallel} >0.2 h~Mpc^{-1}$.  
    %The performance is significantly better at the high frequency subbands of observation. 
    We also find that when combined with the powerful foreground weighting methods used in optimal
    quadratic estimation,
    HERA should be capable of measuring the
    power spectrum at $k_{\parallel} > 0.1$. This study represents a major step toward
    qualifying HERA as a power spectrum instrument and highlights as an
    important method for characterizing instrumental systematics for future
    experiments aiming to detect the 21~cm EoR power spectrum.  
    \end{abstract}

@@

    Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
    emission from neutral hydrogen in our early universe has gained attention as a
    powerful probe of both cosmology and astrophysics.  While the science case for
    21~cm cosmology, particularly during the Epoch of Reionization, is well
    established (see, e.g.,
    ~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
    the technical path toward measuring this signal has been extremely challenging.  The
    weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
    cosmological history, but it also creates sensitivity and calibration
    challenges that are yet to be fully solved.  With noise temperatures dominated
    by sky noise and foregrounds four to five orders of magnitude
    brighter than the signal, 
    sky-averaged 21~cm monopole experiments such as
    EDGES; ~\citep{Bowman_et_al2010},
    BIGHORNS; ~\citealt{2015PhDT........65V},
    SARAS; ~\citep{Patra_et_al2015}, \citep{Patra_et_al2013} ,
    SCIHI; ~\citep{2015PhDT........65V},
    HYPERION; ~\citep{presley_et_al2015}
    % XXX others?
    and 21~cm reionization power spectrum experiments such as
    the LOw Frequency ARray (LOFAR; ~\citealt{van_Haarlem_2013}),
    the Murchison Widefield Array (MWA; ~\citealt{Tingay_2013}),
    the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{Paciga_et_al2011}),
    the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
    the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{deBoer_2016}),
    and the future Square Kilometre Array (SKA; ~\citealt{XXX})
    must furnish both their foreground suppression limits given their system performance at levels significantly
    beyond anything previously achieved in radio telescopes operating below 1 GHz.

    One of the most problematic effects facing these experiments is instrument
    chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
    importance; for line emission, this coordinate translates to a line-of-sight distance
    that can be used to construct three-dimensional maps (and power spectra) of emission,
    as well as probe the evolution of 21~cm emission over cosmological timescales.
    The evolving response of a radio telescope --- either a single dish
    or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
    contaminating spectral modes that might
    otherwise be used to measure reionization ~\citep{liu_et_al2014a}.  Moreover, the chromaticity of
    a telescope's response scales linearly with diameter, putting the
    needs of foreground suppression and signal sensitivity in direct tension with one
    another. In addition to that, systematic effects are unique to each instrument and their manifestation 
    is different in each dataset.

    A major step forward for the field of 21~cm cosmology has been the development
    of a mathematical description of telescope chromaticity, how it varies with
    element separation (or telescope diameter), and what it implies for distinguishing
    foreground emission from the cosmological 21~cm signal~\citep{Thyagarajan_et_al2015}.  The ``wedge'', as it is
    colloquially known, describes a linear relationship between the separation between elements
    in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
    a flat sky and using appropriate
    cosmological scalars,
    the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
    a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
    emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
    $\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
    spectral axis, $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
    that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
    within the limits of the wedge,
    foreground contamination may be suppressed through a combination of calibration and model 
    subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
    wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
    ~\citep{pober_et_al2013},\citep{Thyagarajan_et_al2015}, provided that the spectral responses
    of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
    the chromaticity of the elements in isolation from the chromaticity inherent to
    element separation in an interferometric baseline.}.  In the promising, avoidance-based
    foreground strategy employed by PAPER ~\citep{parsons_et_al2014},\citep{Ali_et_al2015}, these modes
    may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.

    % XXX document map
    The efficacy of the techniques of foreground removal from the measured data
    critically limits the 21~cm power spectrum measurements. The delay
    transformation technique of foreground removal, introduced by
    ~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier
    transform of the visibility measured by an interferometer and produces a
    spectrum, referred to as the delay spectrum hereafter, which is a function of
    the geometric time delay corresponding to the physical length of the baseline
    between two antennas. For the visibilities measured over a wide field across a
    wide frequency bandwidth, the delay spectrum consists of the instrument
    response, the foreground signal, and the 21cm power spectrum, hereafter
    referred to as the EoR signal.
    %The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
    The technique exploits the smooth spectral characteristics of the foreground
    and for a widefield wide bandwidth visibility measurement by an interferometer
    with a baseline $b$, confines the foreground contribution to the computed delay
    spectrum within the largest possible time delay, $\tau = b/c$, corresponding to
    the given baseline length. Such techniques also assume a spectrally smooth
    instrumental response whose contribution to the measured data, much as the
    contribution of the smooth spectrum foreground, also has an upper bound in the
    delay space imposed by the largest geometric delay of the given baseline.
    Beyond this limit, for an ideal system performance, the delay spectrum would be
    dominated by any wideband signal across the sky with spectral and spatial
    fluctuations over small scales, such as the EoR signal, and therefore, could be
    detectable. The interaction between the sky signal and instrument response can
    alter the relative contribution of the foreground, instrument response and the
    EoR signal at a given delay and, thus, influence the detectability of the EoR
    signal. Such interactions may cause the foreground and systematics to spill
    over into higher delays and, thus, push the upper limit of the foreground and
    systematics contaminated delay modes to much higher delays. In this process,
    the EoR signal over large spatial scales will be lost. \\

    \begin{figure*}
    \centering
    \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
    \caption{HERA dish feed at the Green Bank NRAO site.}
    \label{fig:heradish}
    \end{figure*}

    In this paper, we use reflectometry measurements to
    investigate the delay-domain performance of 
    the 14-m parabolic dish elements (Figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
    from 100 to 200~MHz.
    %Reflectometry measurements are carried out across a wide bandwidth on a
    %prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
    %results are interpreted in light of the delay spectrum technique of power
    %spectrum estimation and inverse covariance weighting method of foreground
    %suppression. 
    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
    In this paper, Section 2 briefly describes the delay spectrum for the ideal and
    non-ideal performance of a two element interferometer. Section 3 describes the
    reflectometry measurements and establishes the connection between visibility
    measurements and reflectometry. Reflectometry results are described in Section
    5. Section 6 evaluates the performance of the HERA element for detection of the
    21~cm power spectrum.

@@

    Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,

    \begin{equation}
    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)~\volt_\sky(\thhat,\nu)\nonumber\\
    \end{equation}
    \begin{equation}
    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)~\volt_\sky(\thhat,\nu)~\fngexp\nonumber\\
    \end{equation}
    Hence, the time averaged visibility measured by the interferometer may be written as, 
    \begin{equation}
    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)~  \volt_{2}^{*} (\thhat, \nu)~ \ifngexp d\Omega 
    \label{eq1}
    \end{equation}

@@

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    %\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	  
     \tilde V(\vec b, \tau) & = & \beam(\vec b,\tau)*I_\sky(\vec b,\tau)
                           %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. Qualitatively, 
    delay spectrum of the visibility results from the convolution of the delay spectrum of the instrument with the instrument delay response. It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay. by de-convolving the delay transformed visibility by the instrument response.

>>>>

    \title{THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH III : MEASURING CHROMATICITY OF PROTOTYPE ELEMENT WITH REFLECTOMETRY. } 
    %\maketitle

    \author{
    Nipanjana Patra\UCB\myemail,
    Aaron~R.~Parsons\UCB,
    David~R.~DeBoer\UCB,
    Nithyanandan Thyagarajan\ASU,
    Aaron  Ewall-Wice\altaffilmark{7},
    Gilbert Hsyu\UCB, 
    Tsz Kuk Leung\UCB,
    James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Anna Lebedeva\UCB, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
    }

@@

    \begin{abstract}
    Spectral structures from instrumental systematic effects is the current
    limiting factor for the experiments attempting to detect the redshifted 21~cm
    signal from the Epoch of Reionization (EoR). 
    Recent advances in the delay spectrum methodology for measuring the
    21~cm EoR power spectrum have brought new attention to the impact of
    an antenna's frequency \textbf{response} has on the viability of
    making this challenging measurement.
    %Systematics are specific to
    %instruments and their direct measurement or estimation is not always
    %straightforward. 
    %The Hydrogen Epoch of Reionization Array (HERA) uses the delay
    %spectrum technique for estimating of 21~cm power spectrum. 
    In particular, \textbf{this methodology} provides a somewhat straightforward relationship
    between time-domain reflectometry profiles of an instrument that can be directly
    measured with a vector network analyzer (VNA) and the power spectrum modes accessible
    to a 21~cm EoR experiment.
    %In a unique way, the
    %delay spectrum technique directly translates to reflectometry in case of
    %measuring instrumental response and allows the direct measurement of systematic
    %effects in individual array element.  
    In this paper, we derive the explicit relationship between $S_{11}$ measurements
    made by a VNA and the extent of \textbf{additional foreground contamination in delay space}.
    \textbf{In the light of this mathematical framework}, we examine
    the spectral chromaticity of a prototype antenna element which will
    constitute the Hydrogen Epoch of Reionization Array (HERA) 
    between 100 and 200~MHz.
    These reflectometry measurements exhibit \textbf{additional} structure relative
    to electromagnetic simulations, but we find 
    that even without \textbf{any further design improvement}, such an antenna element
    will support measuring $k$ modes with line-of-sight components of
    $k_{\parallel} >0.2h$ Mpc$^{-1}$.  
    %The performance is significantly better at the high frequency subbands of observation. 
    We also find that when combined with the powerful foreground weighting methods used in optimal
    quadratic estimation,
    HERA prototype elements \textbf{could successfully measure the
    power spectrum at spatial modes as low as $k_{\parallel} > 0.1h$~Mpc$^{-1}$. This study represents a major step towards 
    understanding the HERA antenna element. It also highlights an
    important method for characterizing instrument response for future
    experiments designed to detect the 21~cm EoR power spectrum using a reflector-type antenna. } 
    \end{abstract}

@@

    Since it was first proposed in \cite{1997ApJ...475..429M, Shaver_et_al1999}, \textbf{measurement of redshifted} 21~cm
    emission from neutral hydrogen in our early universe has gained attention as a
    powerful probe of both cosmology and astrophysics.  While the science case for
    21~cm cosmology, particularly during the Epoch of Reionization, is well
    established (see, e.g.,
    ~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
    the technical path toward measuring this signal has been extremely challenging.  The
    weakness of \textbf{the} hyperfine line keeps the 21~cm signal below opacity throughout
    cosmological history, but it also creates sensitivity and calibration
    challenges that are yet to be fully solved.  With noise temperatures dominated
    by sky noise and foregrounds four to five orders of magnitude
    brighter than the signal even in the coldest patches of the sky, 
    sky-averaged 21~cm monopole experiments such as
    EDGES; ~\citep{Bowman_et_al2010},
    BIGHORNS; ~\citealt{2015PhDT........65V},
    SARAS; ~\citep{Patra_et_al2015, Patra_et_al2013} ,
    SCIHI; ~\citep{2015PhDT........65V},
    HYPERION; ~\citep{presley_et_al2015}
    % XXX others?
    and 21~cm reionization power spectrum experiments such as
    the LOw Frequency ARray (LOFAR; ~\citealt{van_Haarlem_2013}),
    the Murchison Widefield Array (MWA; ~\citealt{Tingay_2013}),
    the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{Paciga_et_al2011}),
    the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
    the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{deBoer_2016}),
    and the future Square Kilometre Array (SKA; \footnote{www.skatelescope.org}~\citealt{2013ExA....36..235M})
    must furnish both their foreground suppression limits given their system performance at levels significantly
    beyond anything previously achieved in radio telescopes operating below 1 GHz.

    One of the most problematic effects these experiments face is the instrument
    chromaticity \textbf{that are instrument specific and have unique manifestation in the measured data}.  The spectral dimension of    
    21~cm reionization experiments is of vital
    importance; for line emission, this coordinate translates to a line-of-sight distance
    that can be used to construct three-dimensional maps (and power spectra) of emission,
    as well as probe the evolution of 21~cm emission over cosmological timescales.
    The response of a radio telescope --- either a single dish
    or an interferometer --- versus spectral frequency, modulates spectrally smooth foregrounds,
    contaminating spectral modes that might
    otherwise be used to measure reionization ~\citep{datta_et_al2010, trott_et_al2012, vedantham_et_al2012, 2012ApJ...752..137M, liu_et_al2014a}. \textbf{  Moreover, measurement sensitivity could be increased by increasing the collecting area of the element using reflector structures that  results in increased elementsize.  However, the chromaticity of
  a reflector dish scales with its diameter}, putting the
    needs of foreground suppression and signal sensitivity in direct tension with one
    another. 
    %In addition to that, systematic effects are unique to each instrument and their manifestation 
    %is different in each dataset.

    A major step forward for the field of 21~cm cosmology has been the development
    of a mathematical description of telescope chromaticity, how it varies with
    element separation (or telescope diameter), and what it implies for distinguishing
    foreground emission from the cosmological 21~cm signal~\textbf{\citep{Parsons_et_al_2012, vedantham_et_al2012, trott_et_al2012, 2014PhRvD..90b3018L, 2014PhRvD..90b3019L, 2015PhRvD..91b3002D,nithya_et_al2013,  Thyagarajan_et_al2015}.}  The ``wedge'', as it is
    colloquially known, describes a linear relationship between the separation between elements
    in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
    a flat sky and using appropriate
    cosmological scalars,
    the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
    a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
    emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
    $\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
    spectral axis, $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
    that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
    within the limits of the wedge,
    foreground contamination may be suppressed through a combination of calibration and model 
    subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
    wedge pattern~\textbf{\citep{2016MNRAS.461.3135B}.  Outside of the wedge, foreground contamination drops rapidly 
    ~\citep{pober_et_al2013, 2014PhRvD..89b3002D,  Thyagarajan_et_al2015, Saul_et_al2016}}, provided that the spectral responses
    of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
    the chromaticity of the elements in isolation from the chromaticity inherent to
    element separation in an interferometric baseline.}.  In the avoidance-based
    foreground strategy employed by PAPER ~\citep{parsons_et_al2014, Ali_et_al2015}, these modes
    may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.

    % XXX document map
    The efficacy of foreground removal from the measured data
    critically limits the 21~cm power spectrum measurements. The delay
    transformation technique of foreground removal, introduced by
    ~\citep{Parsons_Backer_2009, Parsons_et_al_2012}, computes the Fourier
    transform of the visibility measured by an interferometer and produces a
    spectrum, referred to as the delay spectrum hereafter, which is a function of
    the geometric time delay corresponding to the physical length of the baseline
    between two antennas. For the visibilities measured over a wide field across a
    wide frequency bandwidth, the delay spectrum consists of the convolution of the instrument
    response with the foreground signal, and the 21cm power spectrum, hereafter
    referred to as the EoR signal.
    %The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
    The technique exploits the smooth spectral characteristics of the foreground
    and for a %widefield wide bandwidth
     visibility measurement by an interferometer
    with a baseline $b$, confines the foreground contribution to the computed delay
    spectrum within the largest possible time delay, $\tau_{g} = b/c$, corresponding to
    the given baseline length. \textbf{In reality, however, foregrounds show a response beyond the maximum geometric delay    
    due to broadband spectrum of the foreground sources and chromatic instrument response. For an ideal system, this 
    is a rapidly diminishing response beyond $\tau_{g}$ spanning the delay range corresponding to the inverse of the  
    measurement bandwidth. }
    Beyond this limit, for an ideal system performance, the delay spectrum would be
    dominated by any signal with spectral and spatial
    fluctuations over small scales, such as the EoR signal.  The interaction between the sky signal and instrument response can
    alter the relative contribution of the foreground, and the
    EoR signal at a given delay and influence the detectability of the EoR
    signal. Such interactions may cause the foreground to spill
    over into higher delays and push the upper limit of the foreground and
    systematics contaminated delay modes to much higher delays \textbf{contaminating the EoR window .} \\
    \begin{figure*}
    \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
    \caption{A prototype HERA element at the Green Bank NRAO site consisting of a crossed dipole feed and a parabolic reflector dish.}
    \label{fig:heradish}
    In this paper, we use reflectometry measurements to
    investigate the delay-domain performance of 
    \textbf{a prototype 14-m parabolic reflector dish and a crossed dipole feed (figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
    from 100 to 200~MHz. For clarity, the return loss of the feed when measured off of the dish will be referred to as ``feed return loss" hereafter. The dish-feed assembly, when the feed is placed at the focal point of the dish is referred to as ``HERA element" hereafter. }
    %Reflectometry measurements are carried out across a wide bandwidth on a
    %prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
    %results are interpreted in light of the delay spectrum technique of power
    %spectrum estimation and inverse covariance weighting method of foreground
    %suppression. 
    This paper is one in a series of five papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}, beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
    In this paper, Section 2 briefly describes the delay spectrum for the ideal and
    non-ideal performance of a two element interferometer. Section 3 describes the
    reflectometry measurements and establishes the connection between visibility
    measurements and reflectometry. Reflectometry results are described in Section
    5. Section 6 evaluates the performance of the HERA element for detection of the
    21~cm power spectrum.

@@

    Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in the direction $\thhat$ \textbf{at a frequency $\nu$} by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,

    \begin{equation}
    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)~\volt_\sky(\thhat,\nu)\nonumber\\
    \end{equation}
    \begin{equation}
    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)~\volt_\sky(\thhat,\nu)~\fngexp\nonumber\\
    \end{equation}

    \textbf{where $\bmvolt_{1}$, $\bmvolt_{2}$ are the voltage gain pattern of the two antennae.}
    Hence, the visibility measured by the interferometer may be written as, 
    \begin{equation}
    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)~  \volt_{2}^{*} (\thhat, \nu)~ \ifngexp d\Omega
    \label{eq1}
    \end{equation}

@@

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    %\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	  
     \tilde V(\vec b, \tau) & = & \beam(\vec b,\tau)*I_\sky(\vec b,\tau)
                           %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. Qualitatively, 
    delay spectrum of the visibility results from the convolution of the \textbf{instrument delay response with the delay spectrum of the sky. It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay by de-convolving the delay transformed visibility by the instrument response. }

   The delay-transformed visibility is related to the power spectrum of redshifted
    21 cm emission by the relation, 
    \begin{equation}
     %P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{$\Omega$\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
     %\end{equation}
     %\begin{equation}
 P_{21}(k_\perp,k_\parallel) \approx |(\tilde V(\vec b, \tau)|^{2} \left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 {X^{2}Y \over \Omega \Delta B}
    \label{eq4}
    \end{equation}
    where
    \begin{equation}
      k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
      k_\parallel = \frac{2\pi\tau\,f_{21}H(z)}{c(1+z)^2}, 
     \label{eq5}
    \end{equation}
